---
title: "Documentation"
author: "Max Rohde"
date: "3/3/2021"
output: html_document
---

```{r}
library(bios6312)
```

The following function are available:

- `get_robust_variance`
- `get_studentized_residuals`
- `qqnorm_studentized_residuals`
- `studentized_residuals_vs_fitted_plot`
- `studentized_residuals_vs_predictors_plot`
- `testparm`
- `lincom`

To get help on any function, you can access the documentation with `?example_function`.

We will use the built-in `mtcars` dataset to demonstrate each function.

```{r}
head(mtcars)
```

```{r}
my_model <- lm(mpg~wt, data=mtcars)

summary(my_model)
```

```{r}
get_robust_variance(my_model)
```

```{r}
get_studentized_residuals(my_model)
```

```{r}
qqnorm_studentized_residuals(my_model)
```

```{r}
studentized_residuals_vs_fitted_plot(my_model)
```

```{r}
studentized_residuals_vs_predictors_plot(my_model)
```


```{r}
my_interaction_model <- lm(mpg ~ wt*cyl, data=mtcars)

summary(my_interaction_model)
```

```{r}
# Replicates the `testparm` function in Stata
# Test if beta2 + beta3 == 0
testparm(par=c(3,4),
         model=my_interaction_model,
         type="F")
```

```{r}
# Replicates the `lincom` function in Stata
# Estimates beta2 + 3.2beta3
lincom(par=c(3,4),
       mult=c(1,3.2),
       model=my_interaction_model)
```

